A Domain Specific Language for SpectreGuard

### 2020-12-07 paper/main.tex
Reformat generated code in paper

\begin{figure}
\begin{lstlisting}{language=C}
int _fs_0[8] __attribute__((nospec))__;
int _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0; _fs_4 < (_fs_0[_fs_2]); _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}{language=C}
int _fs_0[8] __attribute__((nospec))__;
int _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0 ;
      fs_4 < (_fs_0[_fs_2]);
      _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}
